\documentclass[a4paper,12pt]{article}
\usepackage{latexsym}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{wrapfig}
\pagestyle{plain}
\usepackage{fancybox}
\usepackage{bm}

\begin{document}

0.1 Estimation

-in estimates. Taking ?11 0 (see Theorem 1) as an example, an estimate thereof is
\begin{center}
?11,0 (1) $=\displaystyle \frac{1}{\sum_{i=1}^{n}I\{D_{i}=1,M_{i}=0,T_{i}=1\}}\sum_{i:D_{i}=1,M_{i=}0,T_{i=}1}Y_{i}$
$$
-\frac{1}{\sum_{i=1}^{n}I\{D_{i}=1,M_{i}=0,T_{i}=0\}}\sum_{i:D_{i}=1,M_{i=}0,T_{i=}0}\hat{Q}_{00}(Y_{i})\ .
$$
\end{center}
Likewhise, quantile effects are estimated based on the empirical quantiles. For the

estimation of total ATE and QTE, show that the resulting estimators are $\sqrt{N}$-

consistent and asymptotically normal, see their Theorems 5.1 and 5.3. These prop-

erties also apply to our context when splitting the sample into subgroups based on

the values of a binary treatment and mediator (rather than the treatment only).

For instance, the implications of Theorem 1 in when considering subsamples with

$D = 1$ and $D = 0$ carry over to considering subsamples with $D = 1, M = 0$ and

$D=0, M=0$ for estimating the average direct effect on never-takers. In contrast to

, however, some of our identification results include the conditional mediator prob-

abilities $\mathrm{P}\mathrm{r}(M=m|D=d)$ . As the latter are estimated with $\sqrt{N}$-consistency, too,

it follows that the resulting effect estimators are again $\sqrt{N}$-consistent and asymp-

totically normal. We use a non-parametric bootstrap approach to calculate the

standard errors. show the validity of the bootstrap approach for such kind of esti-

mators, which follows from their asymptotic normality. For the case that identifying

assumptions to only hold conditional on observed covariates, denoted by $X$, estima-

tion must be adapted to allow for control variables. Followinga suggestion by in

their Section 5.1, basing estimation on outcome residuals in which the association of

$X$ and $Y$ has been purged by means of a regression is consistent under the additional

assumption that the effects of $D$ and $M$ are homogeneous across covariates. As an

alternative, propose a flexible semiparametric estimator that does not impose such

a homogeneity-in-covariates assumption and show $\sqrt{N}$-consistency and asymptotic

normality.
\end{document}
