\documentclass[a4paper,12pt]{article}
\usepackage{latexsym}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{wrapfig}
\pagestyle{plain}
\usepackage{fancybox}
\usepackage{bm}

\begin{document}

ZENIT (Zero Emission Neighborhood Investment Tool) is

a tool for minimizing the cost of investing and operating the

energy system of a Zero Emission Neighborhood (ZEN). It

uses a MILP model to find the optimal type and size of

technology needed to provide heat and electricity to a ZEN.

The concept contains much more than only the energy system

(materials and architecture to name two examples) but this

tool’s focus is energy systems. The idea behind ZEN is to limit

emissions and that it is possible to compensate for the various

emissions of $CO_{2}$ in the neighborhood by exporting electricity

to the grid. Indeed, by exporting electricity produced from

on-site renewable to the grid, we assume that the production

in the system is reduced by the corresponding amount and

thus reduces the emission of the total system. The model

used in this paper is based on the model presented in . In

this section, the main elements of the model will be repeated

and the differences with the model from presented. For the

details on the model not repeated, one can refer to that paper.

Then the implementation and case chosen will be presented.

The optimization is written in Python and uses Gurobi as a

solver. In this paper, we interpret the definition of a ZEN as

a neighborhood that has $0$ emissions over its lifetime, which

is set to 60 years. However due to practical reasons and to

reduce the computational time, different periods of the lifetime

can be defined using one representative year for each. In this

study we use a single period. The different decision variables

are the amount of investment in each technology for heat,

power and energy storage as well as the operation related

variables defined for each hour (e.g. amount of electricity

produced, amount of fuel consumed). Multiple constraints are

used, to enforce the $CO_{2}$ limitations necessary in the ZEN

context and to represent the operation of the neighborhood

and in particular of each technology. It is important to note

that part load limitations and start up/shutdown constraints are

not implemented. The objective function of the optimization

is the following: {\it Minimize}:

$\displaystyle \sum_{\iota}$ {\it Cidisc} $\cdot x_{i}+b_{hg} \cdot C_{hg}+\displaystyle \frac{1}{\ovalbox{\tt\small REJECT}_{r,D}^{tot}}\sum_{\dot{\iota}}$ {\it Cmaint}$\cdot x_{i}$
$$
+\frac{1}{\ovalbox{\tt\small REJECT}_{r,D}^{tot}}(\sum_{t}(\sum_{f}f_{f,t}\cdot P_{f}^{fuel}+(P_{t}^{spot}+P^{grid}
$$
\begin{center}
$+P^{ret})\displaystyle \cdot(y_{t}^{imp}+\sum_{est}y_{t,e\overline{s}t}^{gbimp})-P_{t}^{spot}\cdot y_{t}^{exp}))$   (1)
\end{center}
Where $C_{i}^{disc}$ is the discounted investment cost in technology

$i$ including re-investments and salvage value, $x_{i}$ the capacity

of technology $i, b_{hg}$ the binary variable for investment in

a heating grid, $C_{hg}$ the cost of the heating grid, e{\it troDt} the

discount factor for the whole lifetime of the neighborhood

with discount rate $\mathrm{r}, C_{i}^{maint}$ the annual maintenance cost,

$f_{f,t}$ the fuel consumption, $P_{f}^{fuel}$ the fuel price, $P_{t}^{spot}$ the

electricity spot price, $P^{grid}$ and $P^{ret}$ the grid and retailer

tariffs, $y_{t}^{imp}$ and $y_{t}^{exp}$ the import and export of electricity from

the neighborhood and $y_{t,\overline{es}t}^{gbimp}$ the import of electricity to the

storage. The subscript $t$ represent timesteps, $i$ the technologies

with in particular $f$ for the technologies using other fuel than

electricity and {\it est} for energy storages. It minimizes the cost

of investing in the different technologies and the operating

costs, fuels, electricity and O\& M costs and contains the costs

of the heating grid and a binary associated with it that also

gives access to technologies at a neighborhood level. The

most important constraint in the case of ZENs is the $CO_{2}$

balance $($??$)$ , whose principle was explained earlier. In $($??$)$ ,

$y_{est}^{gb_{-}imp}, y_{est}^{gb_{-}xp}$ and $y_{t,\overline{es}t}^{pbexp}$ are respectively the import and

export on the grid side battery and the export from the on-

site technologies producing electricity, $\phi_{e}^{CO_{2}}$ and $\phi_{f}^{CO_{2}}$ the

$CO_{2}$ factors for electricity and other fuels, ?{\it est} the efficiency

of battery and $y_{t,g}^{exp}$ the export of electricity from the on-site

technologies.

$\displaystyle \sum((y_{t}^{imp}\ +\ \sum y_{t,\overline{es}t}^{gbimp})\ .\ \phi_{e}^{CO_{2}})$

$t$ {\it est}
$$
+\sum\sum\ (\phi_{f}^{CO_{2}}\ .\ f_{f,t})\ \leq\ \sum(\sum(y_{t,\overline{es}t}^{gbexp}
$$
$t f t$ {\it est}
\begin{center}
$+y_{t,\overline{es}t}^{pbexp}) \cdot$?{\it est} $+\displaystyle \sum y_{t,g}^{exp}$) $\cdot \phi_{e}^{CO_{2}}$   (2)
$$
g
$$
\end{center}
Fig. presents graphically the electricity balance and the differ-

ent equations associated. Different technologies are included

in the study; some of them are only available at the building

level and others at the neighborhood level in a centralized pro-

duction plant. The different technologies are: at the building

level : Solar Panels (PV), Solar Thermal (ST), Heat Pumps

(HP), Biomass Boiler (BB), Electric Boiler (EB), Gas Boiler

(GB); and at the neighborhood levels: CHP $($nCHP) , Gas

Boiler $(\mathrm{n}\mathrm{G}\mathrm{B})$ , Electric Boiler $(\mathrm{n}\mathrm{E}\mathrm{B})$ , Heat Pumps $(\mathrm{n}\mathrm{H}\mathrm{P})$ . In

addition, Batteries (Bat) and Heat Storage (HS) are available

at both levels. Different subcategories can be available to

choose from within each category, for instance air-water or

water-water heat pumps. In parenthesis is the notation used

for the rest of the study for each technology. Unlike the

model in , the model used for this paper uses a disaggregrated

heat load. The buildings’ load are not summed, but types

of buildings are identified and the loads are aggregated per

building type. It is possible to use a completely disaggregated

heat load but the lack of available data motivated not doing

it. The input data necessary to run ZENIT are the electric and

heating loads (ideally separated between domestic hot water

and space heating), the outside and ground temperatures, the

solar insolation and the electricity prices. Hourly timeseries

for each representative years are necessary. A description of

the neighborhood and its buildings with the floor and the roof

area, and the layout of the neighborhoods is also needed. In

this study we assume the heating grid is there (and set the

corresponding binary to 1) because there is one in the location

that inspired this case. Its characteristics (layout, losses and

cost) are then necessary but a module can be used to provide

an estimate of the losses and cost based on the layout of the

neighborhood. The $CO_{2}$ factors used were 17 $\mathrm{g}CO_{2}/\mathrm{k}\mathrm{W}\mathrm{h}$ for

electricity, 277 $\mathrm{g}CO_{2}/\mathrm{k}\mathrm{W}\mathrm{h}$ for gas and 7 $\mathrm{g}CO_{2}/\mathrm{k}\mathrm{W}\mathrm{h}$ for wood

chips . The electricity produced via solar panels or
\end{document}
